Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-06 article.tex
Go towards a four-state Markov chain
Pretty four state Markov chain
Add Bonferroni correction

\begin{figure}
  \centering
  \input{markov_chain.latex}
  \caption{
    State transitions in TMHs caused by mutations, with respect to the
    detection by the immune system. Any TMH is either in a detected, $D$, or
    undetected, $U$, state. Mutations cause state transitions with probability
    $p$. For example, $p_{DU}$ denotes the probability that a detected
    TMH mutates into an undetected one.
  }
  \label{fig:markov_chain}
\end{figure}

@@

When we have calculated the probability of each transition (as described below),
we can simply count the number of observed transitions.
Because the probability of transitions differ per polypeptide,
the total system has the properties of a Poisson binomial distribution,
where, for example, the expected number of transitions is the sum of individual
probabilities. We calculate the probability of the observing our
number of transitions.
If this probability is lower than 5\%, we will state 
that this unlikely situation is most likely caused by natural selection.

>>>>

\begin{figure}
  \centering
  \input{markov_chain_4_states.latex}
  \caption{
    State transitions in TMHs caused by mutations, with respect to the
    detection by the immune system. Any TMH is either in a detected, $D$, or
    undetected, $U$, state. Mutations cause state transitions with probability
    $p$. For example, $p_{DU}$ denotes the probability that a detected
    TMH mutates into an undetected one.
  }
  \label{fig:markov_chain}
\end{figure}

@@

When we have calculated the probability of each transition (as described below),
we can simply count the number of observed transitions.
Because the probability of transitions differ per polypeptide,
the total system has the properties of a Poisson binomial distribution,
from which we can calculate the probability of the observing our
number of transitions.

\paragraph{Hypotheses testing}

Of the complete system, we test for each of the 12 state transitions (that is,
we do not test for mutations that result in the same state).
For each transition rate, we know the expected and observed number
of transitions. If the observed number of transitions is below the expected
value, we test for finding that (low) number of transitions or less.
If the observed number of transitions is above the expected
value, we test for finding that (high) number of transitions or more.
We use a significance level $\alpha$ of 5\%, because we have no prior
evidence. 
As we are testing 12 hypothesis, applying the Bonferroni correction results
in $\alpha_c = \frac{\alpha}{12}$.
If the probability of observing that few/many 
transition is below $\alpha_c$, we will state 
that this unlikely situation is most likely caused by natural selection.
